Assessing the Population-level Conservation Effects of Marine Protected Areas

### 2020-11-22 documents/referee-replies.Rmd

*Thank you, we are glad to hear the reviewer feels this is an important contribution.*

My main concerns on reading the paper are that the methods and results are not clearly enough described.

*1) Although the parameterisation of the simulation model is provided the equations should be included in supplementary. I did visit the github site and the simulator but neither allowed me to find formulations easily. So first off the simulation model needs to be explained in detail in supp methods including equations.*

Thank you for pointing out the lack of sufficient detail on the equations for the simulation model. We have restructured the SI so that the simulation model equations are front  and center (SI Line XX), and clarified our explanations of the equations. We have also expanded our description of the simulation model in the text. We hope this clarifies the structure behind the simulation model.

*2) On a related note I didn't come away with a clear sense of the scenarios used to simulate the potential fish outcomes. For example I have no clear sense how you have simulated spatial patterns of fishing intensity.*

We apologize for the confusion in the simulation scenarios. Given the wide array of scenarios employed, and the word constraints of the paper, we unfortunately could not include a thorough description of every scenario in the main text. We have however included a clearer summary of the simulation in the methods section, highlighting among other key attributes the ways in which we simulate spatial patterns of fishing intensity, which as Referee #2 has noted is a critical variable to consider.

*Similarly, it was not clear to me how you decide which model scenarios are most plausible when conditioning on observed response ratios. Yet conveying the ways in which observed RR could be derived would be useful. There is some discussion of this but not enough to detail. I believe that a good part of the discussion could be removed to make way for this.*

@@

Given the word constraints of the paper, we felt that most of the simulation detail had to be left to Table.XX, Supplemental Information section XX. We agree though that readers would benefit from more clarity in the main text. Given the particularly critical nature of movement and fishing behavior in MPA models, we have included the following statement on line XX of the methods.

XX

*3) The figures are generally not very clear; particularly 2 and 6. In the case of 2 it just isn't visually very clear what's going on and for 6 it requires a more interpretation in the caption to help someone follow it.*

Thank you for pointing this out. We have redesigned Figure 2 to make clearer that the raw data a) support the parallel trends assumption between the targeted and non-targeted populations pre-MPA and b) that the raw data support the statistical finding of no clear MPA effect. We have rewritten the caption to make Figure 6 clearer: we acknowledge that it is a complicated figure but we feel that it is important to convey the range of possible outcomes produced by our simulation model.

Declarative sentance for what this figure is out. Results of ... Insight first, then terms at the end. warmer colors indicate larger effect XX

@@

*After reading just the main text I was left with a few questions about the DiD: how the years were binned (and why those bins)? The year ‘bins’ are in the table and figure 4, but in the methods it says there was a just a pre and post MPA time-period.*

Thank you for pointing this out. We have clarified the pre and post time period discussion in the methods (line XX). We chose to bin the results for visual clarity. At the risk of further expanding the already extensive supplementary materials, we have also included a version with a binwidth of 1 (i.e. no binning) to make clear that our results are not sensitive to the choice of binwidth.

*Also, it seems like MPA status (so inside vs putative ‘control’ sites) should also be a factor in the model, but that wasn’t included? *

This is a very good point. We include hierarchical terms for each site in the data, clustered by the specific island in the Channel Islands a specific site was located at. This serves to control for any intrinsic traits of the MPA sites themselves, e.g. if MPA sites were preferentially placed on better habitat than "control" sites. The site-specific intercept then represents the mean total biomass density of non-targeted species pre-MPA, conditional on the other covariates in the model.

@@

*Was temporal autocorrelation was dealt with/checked for?*

This is a good question. We considered treating the year effects as hierarchichal terms, which would help account for the autocorrelated nature of observations over time. We elected not to, as doing so would negate their benefits as an identification strategy, controlling for unobserved variables that are correlated with with the timing of MPA placement with the total biomass densities of targeted finfish. As discussed in @larsen2018, treating our year terms as hierarchical (or random effects in the context of that paper) means that we assume that the error distribution of the year terms is uncorrelated with the treatment, meaning that the difference-in-difference no longer acts to remove omitted variable bias, which is its main purpose here.

This may mean that we are underestimating the error in our estimated MPA effects, since the model treats observations from different years as conditionally independent. We feel that this would be a more important concern if we had estimated a for example positive but small effect of the MPAs, where perhaps slightly broader error bars might start to span zero. Given that one of our main results is that we are unable to detect a clear signal, we feel that the possible risk of underestimating the error distributions is outweighted by the potential gains of helping control for omitted variable bias.

*Fig 2: can you make the lines a bit narrower?*

We have cleaned up Fig.2 substantially, and hope that the message that the raw data a) support the parallel trends assumption between the targeted and non-targeted populations pre-MPA and b) that the raw data support the statistical finding of no clear MPA effect. We have rewritten the caption to make Figure 6 clearer: we acknowledge that it is a complicated figure but we feel that it is important to convey the range of possible outcomes produced by our simulation model.

@@

*Fig 4: indicate pre-MPA period.*

We have clarified that all the year bins are post-MPA, since the MPAs went in place in 2003, in the figure caption. We worry that given the large amount going on in Figure 4 already adding another shaded area might be confusing.

@@

*189: I don’t think it is overlooked. E.g. see work done on the Great Barrier Reef, where quota management was coordinated with a major MPA rezonining in 2004. Papers by Little in this journal (2009 “Complementarity of No-Take Marine Reserves and Individual Transferable Catch Quotas for Managing the Line Fishery of the Great Barrier Reef”) and Hopf in Current Biology (2016 “Synergistic Effects of Marine Reserves and Harvest Controls on the Abundance and Catch Dynamics of a Coral Reef Fishery”)*

Thank you for pointing this out, and have rephrased this section accordingly (line XX) to reflect that this is something that stakeholders should be aware of, as demonstrated in Little et al. 2009.

@@

*225: I don’t think this simulation study was reported in the methods and results, but should be, or reference given to appendix?*

We believe there is some confusion, this is the same simulation model as presented in the methods (line XX) and used elsewhere in the paper. This clearly was not evident in the text though, we have clarified that this is the same model on line XX.

@@

*228: this paragraph belongs in results.*

We have moved this section to the results.

*Discussion: How would poaching in MPAs affect the interpretation of the difference-in-difference model?*

Interesting question! As we discuss on line XX, what evidence we have is that poaching is of limited concern in the Channel Islands (but clear can be a major issue in many MPAs). However, the presence of poaching should not bias the estimates of the DiD model in any way: if poaching were severe enough so as to render the MPAs completely ineffective, then in theory a DiD model such as the one implemented here would simply estimate that the MPA had no effect, as their would be no difference in the conditional biomass densities of targeted and non-targeted species.

However, poaching might certainly influence ones interpretation of the results. If poaching is rampant but stakeholders are largely unaware of it, a model like this might estimate the the MPAs had no effect (which in that case they might not). Stakeholders might then interpret that as a problem of MPA design, a misunderstanding of the movement dynamics or fishing pressure in the fishery, or any other number of variables, when in fact the problem was simply that the MPA was not actually acting as an MPA.

### 2020-11-22 documents/ovando-et-al-pop-effects-of-mpas.Rmd
better plots

Alternatively, fishers can pursue a  “constant-catch” strategy, where fishers have a catch objective and exert as much (or little) effort as needed to achieve that objective. Subsistence fisheries may use a constant-catch style policy over the short-term, as they seek to ensure that their food needs are met. Constant-catch dynamics might also occur in fisheries with constraining quotas that are not updated after the implementation of MPAs. Fishers pursuing constant catch in areas outside an MPA may have to fish harder to achieve the same catch from a smaller part of the population, causing a population conservation loss under `r percent(1 - positive_outcomes$pp[positive_outcomes$fleet_model == "constant-catch"], accuracy = 1)` of our constant-catch simulations. This is an important scenario to consider (as done so in @little2011b) especially as MPAs are increasingly implemented in quota-managed fisheries [@liu2018].

>>>>

Alternatively, fishers can pursue a  “constant-catch” strategy, where fishers have a catch objective and exert as much (or little) effort as needed to achieve that objective. Subsistence fisheries may use a constant-catch style policy over the short-term, as they seek to ensure that their food needs are met. Constant-catch dynamics might also occur in fisheries with constraining quotas that are not updated after the implementation of MPAs. Fishers pursuing constant-catch in areas outside an MPA may have to fish harder to achieve the same catch from a smaller part of the population, causing a population conservation loss under `r percent(1 - positive_outcomes$pp[positive_outcomes$fleet_model == "constant-catch"], accuracy = 1)` of our constant-catch simulations. This potential negative interaction between constant-catch and MPAs is important risk to consider (as done so in @little2011b) especially as MPAs are increasingly implemented in quota-managed fisheries [@liu2018].
